Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-10-29 accessPEP.Rmd
fixed bite incidence estimates
there was a bug in the way left_joins were happening with duplicate records for each year:/

##### Getting raster of coverage
ctar_metadata <- read.csv("data/ctar_metadata.csv")

@@

```{r get data}
## read in data
ctar_data <- read.csv("data/SaisieRage_DATA_2018-09-21_1755.csv")
ctar_metadata <- read.csv("data/ctar_metadata.csv")
mada_district <- readOGR("data/MadaGIS/MadaPops.shp")
mada_communes <- readOGR("output/communes/communes_extracted.shp")

## catchment data
dist_catchments <- read.csv("output/catchments_district_unmasked.csv", row.names = 1)
names(dist_catchments) <- c("mdg_dis_co", "CTAR", "ttimes_weighted")
comm_catchments <- read.csv("output/catchments_commune_unmasked.csv", row.names = 1)
names(comm_catchments) <- c("mdg_cm_", "CTAR", "ttimes_weighted")

@@

## Getting ctar district and commune
ctar_metadata$ctar_dist <- mada_district$mdg_dis_co[match(ctar_metadata$District, 
                                                           mada_district$district)]
pts <- SpatialPoints(cbind(ctar_metadata$LONGITUDE, ctar_metadata$LATITUDE), 
                   proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
ctar_metadata$ctar_comm <- over(pts, mada_communes)$mdg_cm_
dist_catchments$ctar_in_dist <- ifelse(dist_catchments$mdg_dis_co %in% ctar_metadata$ctar_dist, 1, 0)
comm_catchments$ctar_in_comm <- ifelse(comm_catchments$mdg_cm_ %in% ctar_metadata$ctar_comm, 1, 0)

@@

dist_catchments %>% left_join(select(ctar_metadata, CTAR, exclude, 
                                     color, fill, ctar_dist, LATITUDE, LONGITUDE)) -> dist_catchments
mada_district@data <- left_join(mada_district@data, dist_catchments) ## need this?

## Getting commune covars
## Need: weighted ttimes, pop, ctar_in, exclude
ctar_coords <- cbind(ctar_metadata$LONGITUDE, ctar_metadata$LATITUDE)
comm_catchments %>%
  left_join(select(mada_communes@data, pop = MDG__201, mdg_cm_, district = mtch_ds)) %>%
  left_join(select(mada_district@data, mdg_dis_co, district, ctar_in_dist, dist_catch = CTAR, exclude,
                   color, fill, ctar_dist)) -> comm_data
mada_communes@data %>%
  mutate(long = coordinates(mada_communes)[, 1], 
         lat = coordinates(mada_communes)[, 2]) %>%
  select(commune, mdg_cm_, mtch_ds, long, lat) %>%
  right_join(comm_data) %>%
  mutate(distance = apply(distm(select(., long, lat), ctar_coords), 1, min)/1000) -> comm_data
comm_data <- filter(comm_data, ttimes_weighted != "Inf")

## Getting district covars
district_coords <- coordinates(mada_district)
distance_mat <- distm(district_coords, ctar_coords)
mada_district$dist_min <- apply(distance_mat, 1, min)/1000
mada_district@data %>%
  select(district = mdg_dis_co, dist_name = district, pop = pop2015adj, 
         ttimes_weighted_dist = ttimes_weighted, 
         dist_catch = CTAR, distance = dist_min, exclude, color) -> dist_data

>>>>

@@

```{r get data}
## read in data
ctar_data <- read.csv("data/raw/bitedata/peripheral/SaisieRage_DATA_2018-09-21_1755.csv")
ctar_data$district <- gsub("D", "", ctar_data$district, fixed = TRUE)
ctar_metadata <- read.csv("data/raw/ctar_metadata.csv")
mada_district <- readOGR("data/processed/shapefiles/mada_districts.shp")
mada_communes <- readOGR("data/processed/shapefiles/mada_communes.shp")

@@

## Getting ctar district and commune
ctar_metadata$ctar_dist <- mada_district$distcode[match(ctar_metadata$District, 
                                                           mada_district$ADM2_EN)]
pts <- SpatialPoints(cbind(ctar_metadata$LONGITUDE, ctar_metadata$LATITUDE), 
                   proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
ctar_metadata$ctar_comm <- over(pts, mada_communes)$ADM3_PCODE

@@

## Getting commune covars
## Need: weighted ttimes, pop, exclude
ctar_coords <- cbind(ctar_metadata$LONGITUDE, ctar_metadata$LATITUDE)
mada_communes@data %>%
  select(ttimes_weighted = ttms_wtd, pop, mdg_cm_ = ADM3_PCODE, distcode = ADM2_PCODE) %>%
  left_join(select(mada_district@data, distcode, dist_catch = ctch_ttwtd)) -> comm_data

mada_communes@data %>%
  mutate(long = coordinates(mada_communes)[, 1], 
         lat = coordinates(mada_communes)[, 2]) %>%
  select(commune, mdg_cm_, mtch_ds, long, lat) %>%
  right_join(comm_data) %>%
  mutate(distance = apply(distm(select(., long, lat), ctar_coords), 1, min)/1000) -> comm_data
comm_data <- filter(comm_data, ttimes_weighted != "Inf")

## Getting district covars
mada_district@data %>%
  select(district = distcode, dist_name = ADM2_PCODE, pop, 
         ttimes_weighted_dist = ttms_wtd, 
         dist_catch = ctch_ttwtd, distance = dist_cent) -> dist_data
dist_data$exclude <- ctar_metadata$exclude[match(dist_data$dist_catch, ctar_metadata$CTAR)]
